---
title: "Weekly report of animal performance"

subtitle: "(**protocol**: alt sound categorization catch, **experimenter**: `r params$exp_ASCC`)"

output: html_document


params:
  exp_ASCC: NA
  stg_ASCC: NA
  fil_ASCC: NA
  ani_ASCC: NA
  dt_ASCC: NA
  
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  # - \usepackage{tabu}
  # - \usepackage{threeparttable}
  # - \usepackage{threeparttablex}
  # - \usepackage[normalem]{ulem}
  # - \usepackage[normalem]{ulem}
  - \usepackage[utf8]{inputenc}
  - \usepackage{makecell}
  - \usepackage{xcolor}


---

<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
      font-family: "Arial", Helvetica, sans-serif;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 38px;
  font-family: "Arial", Helvetica, sans-serif;
  color: #4d4e4f;
}
h1 { /* Header 1 */
  font-size: 28px;
  font-family: "Arial", Helvetica, sans-serif;
  color: #2c3a3e;
}
h2 { /* Header 2 */
  font-size: 22px;
  font-family: "Arial", Helvetica, sans-serif;
  color: #2c3a3e;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Arial", Helvetica, sans-serif;
  color: #2c3a3e;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>





 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(kableExtra)

MeanWithSD <- function(x){
  paste0(
      mean(x) %>% round(2),
      " ", 
      intToUtf8(177),
      " ",    
      sd(x) %>% round(2)
      )
}

```

<br><br>

# Summary of last 10 day's performance

```{r}
TRAINING %>%
            dplyr::filter(
              experimenter == params$exp_ASCC,
              choice_direction == "right_trials",
              protocol == "@AltSoundCategorizationCatch",
              date <= max(date), date > max(date)-9
            ) %>%
  mutate(correct_ratio = (correct_trials / completed_trials) %>%
           round(2)) %>%
  mutate(violation_ratio = (violation_trials / all_trials) %>%
              round(2)) %>% 
  select(
    animal_id,
    date,
    stage,
    correct_trials,
    error_trials,
    violation_trials,
    timeoout_trials,
    correct_ratio,
    violation_ratio
    ) %>% 
  dplyr::group_by("Animal" = animal_id, "Training phase" = stage) %>% 
  dplyr::summarise(
    #"Training phase" = unique(stage),
    "Mean correct" = MeanWithSD(correct_trials),
    "Mean error" = MeanWithSD(error_trials),
    "Mean violation" = MeanWithSD(violation_trials),
    "Mean timeout" = MeanWithSD(timeoout_trials),
    "Mean correct ratio" = MeanWithSD(correct_ratio),
    "Mean violation ratio" = MeanWithSD(violation_ratio)
    ) %>% 
  datatable(options = list(dom = "t"))
  # knitr::kable(format = "latex", booktabs = T) %>% 
  # kable_styling(latex_options = c("scale_down", "striped"))
```

<br><br>

# Number of completed trials

```{r, fig.width=12, fig.height=10}
plots_AltSoundCategCatch(
      plottype_ASCC = "No. completed trials",
      #datelim_ASCC = params$dt,
      stage_filter_ASCC = params$stg_ASCC,
      f_options_ASCC = params$fil_ASCC,
      animal_filter_ASCC = params$ani_ASCC,
      exp_ASCC = params$exp_ASCC
    )
```


<br><br>

# Number of correct trials

```{r, fig.width=12, fig.height=10}
plots_AltSoundCategCatch(
      plottype_ASCC = "No. correct trials",
      #datelim_ASCC = params$dt,
      stage_filter_ASCC = params$stg_ASCC,
      f_options_ASCC = params$fil_ASCC,
      animal_filter_ASCC = params$ani_ASCC,
      exp_ASCC = params$exp_ASCC
    )
```


<br><br>

# Ratio of correct trials

```{r, fig.width=12, fig.height=10}
plots_AltSoundCategCatch(
      plottype_ASCC = "Correct ratio",
      #datelim_ASCC = params$dt,
      stage_filter_ASCC = params$stg_ASCC,
      f_options_ASCC = params$fil_ASCC,
      animal_filter_ASCC = params$ani_ASCC,
      exp_ASCC = params$exp_ASCC
    )
```
